CLT extension visuals

### 2022-05-17 analysis/clt_item_selection.Rmd
add visuals file

# params_order_p <- params_order%>%
#   group_by(nlpar)%>%
#   mutate(sd = sd(order_dif), 
#          cut_low = mean(order_dif)-2*sd,
#          cut_high = mean(order_dif)+2*sd)
# 
# ggplot(params_order_p, aes(x = order_dif))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_histogram(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# 
# ggplot(params_order_p, aes(x = order_dif, label = item, y = reorder(item, abs(order_dif))))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_point(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# exclude_order <- params_order_p%>%
#   filter(order_dif < cut_low | order_dif > cut_high)%>%
#   pull(item)
# 
# 
# model_params <- all_model_params%>%
#   filter(!item %in% exclude_sex,
#          !item %in% exclude_order)
```

@@

sim_size%>%
  ggplot(aes(x = factor(size), y = cor))+
  geom_point(pch = 1)+
  geom_line(aes(group = factor(iter), lty = factor(iter)))+
  scale_linetype(name = "Run")+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

@@

@@

>>>>

# params_order_p <- params_order%>%
#   group_by(nlpar)%>%
#   mutate(sd = sd(order_dif), 
#          cut_low = mean(order_dif)-2*sd,
#          cut_high = mean(order_dif)+2*sd)
# 
# ggplot(params_order_p, aes(x = order_dif))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_histogram(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# 
# ggplot(params_order_p, aes(x = order_dif, label = item, y = reorder(item, abs(order_dif))))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_point(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# exclude_order <- params_order_p%>%
#   filter(order_dif < cut_low | order_dif > cut_high)%>%
#   pull(item)
# 
# 
model_params <- all_model_params%>%
  filter(!item %in% exclude_sex)
```

@@

saveRDS(sim_size, "../saves/sim_size.rds")

sim_size%>%
  group_by(size)%>%
  summarise(mean_cor = mean(cor),
         min = min(cor),
         max = max(cor))%>%
  ggplot(aes(x = factor(size), y = mean_cor))+
  geom_pointrange(aes(ymin=min, max = max), pch = 1)+
  geom_line(aes(group = 1))+
  scale_linetype(name = "Run")+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

@@

saveRDS(sim_size_age, "../saves/sim_size_age.rds")

@@

saveRDS(frq_sel_items, "../saves/selected_items.rds")

### 2022-05-17 analysis/clt_visuals.Rmd
add visuals file

---
title: "CLT extension visuals"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
```

```{r}
data <- read_csv("../data/clt_clean_data.csv")%>%
  filter(age_group != 8)

@@

icc3 <- readRDS("../saves/icc_3PL.rds")
```

>>>>

---
title: "CLT extension visuals"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(readxl)
library(geomtextpath)
library(ggridges)
```

```{r}
data <- read_csv("../data/clt_clean_data.csv")%>%
  filter(age_group != 8)%>%
  left_join(read_xlsx("../data/clt_new_words.xlsx")%>%
              mutate(aoa_german_comb = str_replace(aoa_german_comb, "\\,", "\\."),
                     aoa_german_comb= as.numeric(aoa_german_comb), 
                     complexity_score = `Complexity score`)%>%
              select(german, word_freq, complexity_score))

@@

icc3 <- readRDS("../saves/icc_3PL.rds")

frq_sel_items <- readRDS("../saves/selected_items.rds")

sim_size <- readRDS("../saves/sim_size.rds")

sim_size_age <- readRDS("../saves/sim_size_age.rds")

params_joy <- readRDS("../saves/model_params_irt3_draws.rds")
```

# Data descriptives

```{r}
p2 <- data%>%
  group_by(source,subjID, age)%>%
  tidyboot_mean(col = correct)

page <- ggplot(p2, aes(x = age, y = mean))+
  #stat_cor()+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #geom_point(alpha = .25)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .5, size = .25)+
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
  labs(x = "Participant age", y = "Proportion correct (by participant)")+
  ylim(0,1)+
  xlim(3,8)+
  theme_few()
```

```{r}
p1 <- data%>%
  group_by(targetWord, aoa_german_comb, word_freq, complexity_score,german)%>%
  tidyboot_mean(col = correct)

# p1%>%
#   ungroup()%>%
#   filter(!is.na(word_freq))%>%
#   mutate(aoa_german_comb = scale(aoa_german_comb), 
#          word_freq = scale(word_freq), 
#          complexity_score = scale(complexity_score))%>%
#   pivot_longer(cols = c(aoa_german_comb, word_freq, complexity_score), names_to = "measure", values_to = "score")%>%
# ggplot(aes(x = score, y = mean))+
#   stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.2)+
#   geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75, pch = 1)+
#   facet_grid(~measure)+
#   #geom_textpath(aes(label = german), hjust = -.2) +
#   #geom_point( alpha = .75)+
#   geom_smooth(method = "lm", alpha = .25)+
#   labs(x = "Comparison score (scaled)", y = "Proportion correct")+
#   ylim(0,1)+
#   theme_few()

paoa <- p1%>%
ggplot(aes(x = aoa_german_comb, y = mean))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r",label.y = 0.85)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75, pch = 1)+
  #facet_grid(~measure)+
  #geom_textpath(aes(label = german), hjust = -.2) +
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm", col = "firebrick", alpha = .25)+
  labs(x = "Age of acquisition (adult rated)", y = "Proportion correct (by item)")+
  ylim(0,1)+
  theme_few()
```

```{r}
ggarrange(page, paoa, ncol = 1)
```
```{r}
ggsave("../graphs/data_fig.png", width = 4, height = 6, scale = 1.25)
```

```{r}
picc <- icc3 %>% 
  mutate(select = ifelse(item %in% frq_sel_items,"yes", "no"),
         pos = as.numeric(as.factor(item)))

iccp <- ggplot(picc%>%filter(select == "yes"), aes(x = theta, y = p,group = item)) +
  #geom_line(alpha = .5) +
  geom_line(data = picc%>%filter(select == "no"), aes(x = theta, y = p,group = item), col = "grey", alpha = .5)+
  #geom_line(aes(x = theta, y = p,group = item, col = item))+
  geom_textline(aes(label = item, col = item),  gap = T, size = 3) +
  #geom_texthline(yintercept = 0.25, lty = 3, alpha = .75, label = "guessing",hjust = 0.8)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #facet_wrap(~group)+
  guides(col = F)+
  scale_color_viridis_d()+
  labs(#title = "ICCs for selected items",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_few()
```

```{r}
pss <- sim_size%>%
  group_by(size)%>%
  summarise(mean_cor = mean(cor),
         min = min(cor),
         max = max(cor))

pssa <- sim_size_age%>%
  group_by(size, age_group)%>%
  summarise(mean_cor = mean(cor),
         min = min(cor),
         max = max(cor))

psel <- ggplot()+
  geom_vline(xintercept = 20, alpha = .5, col = "#31493C")+
  geom_pointrange(data = pssa,aes(x = size, y = mean_cor,ymin=min, max = max, col = factor(age_group)),pch = 1, alpha = .5)+
  geom_line(data = pssa, aes(group = factor(age_group), x = size, y = mean_cor, col = factor(age_group)), alpha = .5)+
  geom_pointrange(data = pss,aes(x = size, y = mean_cor,ymin=min, max = max),pch = 1)+
  geom_line(data = pss, aes(group = 1, x = size, y = mean_cor))+
  scale_linetype(name = "Run")+
  scale_x_continuous(breaks = c(5,10,15,20,25,30,35,40))+
  scale_color_ptol(name = "Age group")+
  theme_few()+
  ylim(0.6, 1)+
  theme(legend.position = c(.8,.4))+
  labs(x = "No. of items in subset", y = "Correlation with full test")
```

```{r}
pparam <- all_model_params%>%
  filter(item %in% frq_sel_items)%>%
  mutate(nlpar = factor(nlpar, levels = c("Easiness", "Discrimination")))%>%
  ggplot(aes(reorder(item, -Estimate), col = item, Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap(~nlpar, scales = "free_x") +
  scale_color_viridis_d()+
	geom_pointrange(pch = 1) +
	coord_flip() +
  guides(col = F)+
	labs(x = "Target word")+
  theme_few()

pparam2 <- params_joy%>%
  left_join(all_model_params)%>%
  filter(item %in% frq_sel_items)%>%
  mutate(nlpar = factor(nlpar, levels = c("Easiness", "Discrimination")))%>%
  ggplot( aes(y = reorder(item, -Estimate), x = val, fill = item))+
  geom_density_ridges(size = 0.2,scale = 4, alpha = .5)+
  facet_grid(~nlpar, scales = "free_x")+
  labs(y = "Target word", x = "Estimate")+
  scale_fill_viridis_d()+
  guides(fill = F)+
  theme_minimal()
```

```{r}
ggarrange(
          ggarrange(psel,pparam2, ncol = 1, labels = c("A","B"), heights = c(1,1.2)),iccp,
          widths = c(1,1.5), labels = c("","C"))

ggarrange(
          ggarrange(psel,pparam, ncol = 1, labels = c("A","B"), heights = c(1,1)),iccp,
          widths = c(1,1.5), labels = c("","C"))
```

```{r}
ggsave("../graphs/item_fig.png", width = 12, height = 5, scale = 1.25, bg = "white")
```
